IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/abstract.tex

\begin{abstract}
Many important security problems in JavaScript, such as browser extension
security, untrusted JavaScript libraries and
safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
of information flow control.
We formally define a system in which a coarse-grained dynamic IFC system
can be designed once and then applied to any programming language
for which external effects can be controlled.  We use
this formalism to implement two IFC systems for JavaScript, and show how
it applies to other languages such as C.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have interference by relating them to their fully isolated variants.
\end{abstract}

>>>>

\begin{abstract}
Many important security problems in JavaScript, such as browser extension
security, untrusted JavaScript libraries and
safe integration of mutually distrustful websites (mash-ups), may be effectively addressed using an efficient implementation
of information flow control.
We formally define a system in which a coarse-grained dynamic IFC system
can be designed once and then applied to any programming language
for which external effects can be controlled.  We use
this formalism to implement two IFC systems for JavaScript, and show how
it applies to other languages such as C.
We describe how this methodology offers design principles for
the construction of information flow control systems in more
traiditional settings, as well as compositional proofs for optimized
concrete implementations of IFC systems, which can be shown to
have non-interference by relating them to their fully isolated variants.
\end{abstract}
